Universal Anonymous Signatures

### 2022-06-23 prism-backend/research/gsac/formal-uas.tex
More passes.

The main contribution of this section is giving a simple syntax and model that
still allow spanning a wide variety of related schemes. We combine aspects of GS
and AC schemes, generalizing whenever possible. Like in ACs, there are multiple
issuers, and each user can get one or more credentials from any of them; and,
also, use more than one credential simultaneously to produce a signature. We
incorporate openers, as in GSs, but there is no tight relationship between
issuer and opener. As a consequence, signers (potentially along with verifiers)
may choose, on a per-signature basis, the policies governing the utility
information extractable from a signature. Signing and verification are
non-interactive processes like in GS schemes, but we show how to convert to an
interactive one as in ACs. Finally, we incorporate functions that allow
tweaking the conditions checked at credential issuance and signature generation
times, including the information that an opener will be able to extract from a
signature. This flexibilizes the scheme even beyond the loose relationship
between issuer and opener.

@@

@@

\paragraph{Anonymity.} %
\iffalse
Informally, anonymity must capture two requirements: (1) interactive credential
issuance protocols do not leak any information about the user requesting them;
and (2) signatures do not leak any information about the signer. In both cases,
any leakage must be limited to whatever the user decides to reveal, for
instance, through arbitrary predicates on the attributes of the credentials used
for issuance and signing. We follow a simulation-based approach to capture this.
Basically, the adversary is challenged to distinguish between real and ideal
executions. In both worlds, the adversary can generate and corrupt honest users,
issuers, and openers. Then, in the real world, the adversary has access to
oracles that allow requesting credentials on behalf of honest users, create
signatures by honest users, and open signatures by honest users. In the ideal
world, these three oracles are replaced by simulated counterparts, which produce
outputs independent of the users' secrets. This formulation is given in
\figref{fig:exp-uas-simanon}, where $\Osimanon = (\lbrace\HU,\CU\rbrace\GEN,
\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\WREG)$.

\begin{figure}[htp!]

  \centering
  \procedure[linenumbering]{$\ExpSimAnonb(1^\secpar)$}{%
    \pcif b = 0: \\
    \pcind \parm \gets \Setup(1^\secpar) \\    
    \pcind b^* \gets \adv^{\Osimanon,\OBTAIN,\SIGN,\OPEN}(\parm) \\
    \pcelse: \\
    \pcind (\parm,\NIZKtrap) \gets \SIMSETUP(1^\secpar) \\
    \pcind b^* \gets \adv^{\Osimanon,\SIMOBTAIN,\SIMSIGN,\SIMOPEN}(\parm) \\    
    \pcreturn b^*
  }

  \caption{Simulation-based anonymity experiment for \UAS schemes.}
  \label{fig:exp-uas-anonb}
\end{figure}

\begin{definition}{(Anonymity of \UAS)}
  \label{def:sign-anonymity-uas}  
  We define the advantage \AdvSimAnon of $\adv$ against \ExpSimAnonb as
  $\AdvSimAnon=|\Pr\lbrack\ExpSimAnono(1^\secpar)=1\rbrack-
  \Pr\lbrack\ExpSimAnonz(1^\secpar)=1\rbrack|$.
  %
  An \UAS scheme satisfies simulatable anonymity if there exists simulators
  \SIMSETUP, \SIMOBTAIN, \SIMSIGN and \SIMOPEN such that, for any p.p.t.
  adversary $\adv$, \AdvSimAnon is a negligible function of $1^\secpar$.
\end{definition}
\fi
We need to ensure that no information is leaked about users requesting a
credential, nor about signers. The latter is typically captured in group
signatures by letting the adversary request challenge signatures, produced
by a challenge user picked randomly out of two users chosen by the adversary,
and requiring the adversary to guess which one was used. In what is frequently
called CCA-like anonymity, the adversary is given access to the opener,
except for challenge signatures. We follow this approach in what we call
signature anonymity. We need however to restrict that challenge signatures
produce the same \yeval value, to prevent trivail wins by the adversary. On
the other hand, since it is possible that both challenge signatures produce
the same \yinsp value, we can model a stronger CCA-like variant, in which the
adversary is allowed to open challenge signatures for the cases in which the
\yinsp value is the same for both challenge users.

In addition to signature anonymity, we need to take into account that, as in
some anonymous credential schemes, a single user may have multiple credentials.
Moreover, these credentials can be obtained from different issuers, or from the
same issuer but for different attributes. Thus, it seems logical to require that
the adversary cannot determine whether any two credential requests originate
from the same signer, or not. To model this, we define the issuance anonymity
game. Intuitively, we let the adversary obtain challenge credentials on behalf
of two honest challenge users, but without knowing to which concrete challenge
user we actually issue the produced credentials. To prevent trivial wins, we
have to make additional restrictions. Namely, the two sets of challenge user and
supporting credentials for requesting the challenge credential need to satisfy
the same issuance policy, and these supporting credentials cannot include
credentials that have been obtained via the conventional \OBTAIN oracle.
The adversary is then allowed to interact with all the other oracles (except the
one producing challenge signatures, which is not needed), with the only further
constraint that any call to the \SIGN oracle that leverages challenge
credentials cannot specify the user identifier (the oracle ``knows'' which one
out of the two challenge users it needs to use). As usual, after interacting in
an arbitrary way with the oracles, the adversary needs to guess the bit $b$
defining which challenge user was employed to produce the challenge credentials.

@@

\begin{figure*}[htp!]
  \centering
  \scalebox{0.9}{
    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\ExpIssAnonb(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        b^* \gets \adv^{\OIssAnon} (\status,\parm) \\
        \pcreturn b^*
      }
    \end{minipage}

    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\ExpSigAnonb(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        b^* \gets \adv^{\OSigAnon} (\status,\parm) \\
        \pcreturn b^*
      }
    \end{minipage}
  }
  \caption{Issuance and signature anonymity experiments for \UAS schemes.}
  \label{fig:exp-uas-anonb}
\end{figure*}

@@

\paragraph{Discussion on the generality of anonymity in \UAS schemes.} %
% This notion of anonymity is more general than that of group signatures in the
% sense that calls to the \OPEN oracle reveal an arbitrary function of the
% identity of the user -- which can certainly be the member index itself, as it
% is frequent in group signatures, or any other function computable from the
% user key, its credentials, and signed message. Moreover, note that
% our notion is even stronger than the conventional ``CCA-like'' anonymity notion
% that gives the adversary access to the open oracle, only restricting it when
% trying to open challenge signature. Precisely the introduction of generic
% opening functions allows us to let the adversary open challenge signatures
% $\csig_b$ as long as the counterpart $\csig_{1-b}$
% makes \Open produce the same \y value as output. This is certainly not
% possible when using conventional opening, since it directly outputs the identity
% of the signer -- which cannot be the same for different challenge users.

% Note that we could actually remove the requirement that the evaluation function
% has to produce the same output on both challenge user-credentials pairs.
% However, by doing so, we would force all constructions to maintain private the
% output of \feval. We opt not to require that, though, as it directly allows
% our model to cover interesting use cases -- such as restricting to selective
% disclosure, or privacy-preserving variants of functional signatures \jdv{check
%   the latter}, although we show how to do that in \secref{sec:transformations}.

\paragraph{Unforgeability.} In anonymous credentials, unforgeability requires
that no adversary can succeed in a credential presentation for attributes that
are not contained in a legitimately issued credential (set) it controls. Note
that, for this, assuming honest issuers is essential as, otherwise, the
adversary can get credentials on any attribute set it wants.
%
The somehow equivalent property in group signatures, inasmuch it also requires
honest issuers, is traceability. It captures the security of the
open-related functionality (e.g., \Open and \Judge) over signatures
that produced by potentially malicious signers, in the presence of an honest
issuer. In a nutshell, it ensures that every signature accepted by
the verification algorithm must have been created by a user who joined the
group, and that the result of \Open (and thus, \Judge) over such a valid
signature is consistent with its signer. With conventional opening, this is
essentially checked by requesting the adversary to produce a signature,
obtaining -- via open -- the ``identifier'' of the user who produced the
signature. Schemes
that do not have conventional opening resort to more subtle techniques, like
matching keys extracted during join transcripts, with keys used for signing
(see, e.g., \cite{dl21}). Thus, even though for more subtle reasons (the need
for reliable bookkeeping during joins) than for anonymous credentials, honest
issuers are required for traceability of group signatures too.

In our \UAS scheme we allow users prove claims over the attributes they
own -- attested via obtained credentials -- through the \feval function.
Roughly, we capture this as in unforgeability requirement of anonymous
credentials. Namely, we check that the \yeval value returned by \Sign along with
the signature, matches the expected one from the specified \feval function.
On the other hand, the opening capabilities of \UAS schemes also call for a
traceability-like property. However, note that, as opposed to group signatures,
$\langle \Obtain,\Issue \rangle$ protocols are over credentials rather than
users -- although, ultimately, credentials must be owned by some user.
Furthermore, since \Open
does not return the actual identity of the signer, but a function \finsp of it
(and other arguments), we need to make sure that the output of \Open
matches the output of \finsp. As in group signatures with non-conventional open,
we resort to extraction-based techniques. All this is captured via \ExpForgeSign
in \figref{fig:exp-uas-unfor-issue}. Therein, the adversary is challenged to
produce a signature $(\sig,\yeval)$ over message \msg and for evaluation
function \feval; as well as the identifiers for the opener (\oid) and
credential issuers (\siid) used to compute the signature. As in traditional
group signatures, the adversary wins if the signature is accepted by \Verify,
yet \Open or \Judge fail. Then, the game extracts the user key and
credentials used to produce the signature. From it, the game checks if the
output of \feval matches the \yeval value produced by the adversary -- this
mimics the behaviour of unforgeability in anonymous credentials. Finally, the
game also checks that the output of \Open (even if accepted by \Judge)
matches the output of \finsp. If there is any mismatch in the last two checks,
or some of the credentials used to produce the signature do not correspond to
the secret key that was allegedly used to request them, the adversary wins the
game.

Our \UAS scheme includes yet another generalisation that requires unforgeability-like
security, though. Concretely, the issuance function \fissue. We need to make
sure that no credential is issued unless its corresponding
request meets the defined issuance policy. From the point of view of group
signatures, this may seem redundant. After all, if all valid signatures produce
consistent evaluation and opening results, given the employed user key,
credentials, and signed message, the notion of traceability seems to be
satisfied. However, from the point of view of anonymous credentials, an attacker
being able to obtain a credential, even when it does not meet the required
conditions to have it issued, is clearly problematic: it would allow to prove
claims over attributes it does not really ``own'' (even if the output of \Sign
and \Open are consistent with the values returned by \feval and \finsp, and
the credential was obtained via an $\langle \Obtain,\Issue \rangle$ run). To
capture this, we define the \ExpForgeIssue experiment. In the experiment, the
adversary is challenged to produce a credential identifier that must be
associated to an existing $\langle \Obtain,\Issue \rangle$ interaction -- thus,
the corresponding \trans entry must exist (which we can check, as the issuer is
honest). The adversary wins if, either the extraction process fails, or the
extracted user secret key and credentials make the corresponding issuance
function fail.

For both \ExpForgeIssue and \ExpForgeSign, the adversary is given access to the
oracle set $\Oforgeissue = \Oforgesign \gets \lbrace\HU,\CU\rbrace\GEN,\IGEN,
\OGEN,\OCORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN$.

@@

\paragraph{Discussion on the generality of unforgeability in \UAS schemes.} %
% The notion of signature unforgeability we present for \UAS is strictly more
% general than the corresponding one of traceability for group signatures. This is
% again a direct consequence of the fact that \Open can return an arbitrary
% function of the signer's key and credentials (and signed message), which is a
% strict generalization of the conventional \Open. Although, even in that case, we
% need to take into account attributes, and the fact that the same user may obtain
% multiple credentials (that is why, even when having \Open return the identity of
% the signer, our notion is not exactly the same). In this sense, the sign
% unforgeability notion for \UAS is equivalent to that of anonymous
% credentials. It would seem, though, that we do not need the traceability part of
% group signatures; after all, it is the protection against wrong claims on
% attributes what enables meaningful and flexible authentication. However, the
% type of protection against misuses of the open functionality that we can
% get with an honest issuer (as in traceability) is much higher than without an
% honest issuer (as in non-frameability). Specifically, with an honest issuer we
% can ensure that the adversary cannot even alter the value returned by \Open on
% signatures by corrupt users, nor the output of the signing predicate \feval.
% Whereas, with a corrupt issuer, all we can ensure is that
% the adversary cannot forge a signature from an honest user for which \Open
% returns the same value as a signature by that honest user would produce; and,
% certainly, a corrupt issuer can arbitrarily issue credentials meeting any
% desired predicate \feval. Signing unforgeability is, therefore, a core property
% to ensure accountability.

% Similarly, by adding the related notion of issuance unforgeability, we ensure
% that no credential can be issued that did not meet the corresponding issuance
% policy. This is again something not necessary in group signatures (with
% verifiable openings), where \Judge accepting the opening proof implies that
% there is a valid join transcript associated to the membership credential used
% to produce the signature. However, in \UAS, given that the credentials contain
% attributes, even though that transcript exists, we need to make sure that the
% issuance policy over these attributes was satisfied -- and this is not something
% (easily) extractable from the signature.

\paragraph{Non-frameability.} %
The notion of non-frameability in \UAS schemes is unavoidably more subtle than
in group signatures. To see this, we note that, by allowing arbitrary
evaluation and open functions to be used, it can be perfectly valid to
have a signature produced by a corrupted user output the same \yeval or \yinsp
values than the ones output when evaluating or opening a signature by an honest
user. As a concrete example, imagine an open function that returns the
nationality of the signer. In any country, there will be many users (corrupt or
not) sharing nationality.
%
More generally, since the issuer is dishonest in non-frameability properties
and, in \UAS, the value produced by \Open may depend on the attributes
included in user credentials, the adversary may even be able to just produce
``legitimate'' openings that output any desired value.

Thus, we again need to resort to extraction techniques. In the non-frameability
definition for \UAS, given in experiment \ExpNonframe in
\figref{fig:exp-uas-frame}, the adversary is challenged to produce a signature
and opening proof that is accepted by \Verify and \Judge, respectively. From
the signature, we then extract the secret key of the signer, and match it
against the secret keys of the honest users. The adversary wins if there is a
match and the signature has not been queried to \SIGN, or if the value \yinsp
output by the adversary is accepted by \Judge, yet it is different from the
extracted $\yinsp'$ value. In the game, the
adversary has access to the oracles in $\Oframe \gets \lbrace\HU,\CU\rbrace\GEN,
\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\WREG,\OBTAIN,\SIGN$.

@@

\paragraph{Discussion on the generality of non-frameability in \UAS schemes.} %
% Anonymous credentials do not have non-frameability property and, thus, it is
% hard to make a comparison. However, we can draw some connections with AC schemes
% that support revocation, as revocation is somehow equivalent to linking, which
% is a type of inspection available in group signatures. In this sense, note that
% basic revocation (without straight deanonymization) can be trivially achieved
% through our generic \Open function. For instance, one could set \finsp to
% be a pseudorandom number seeded with the user's public key (or credential). In
% this sense, \Open could be essentially seen as a Verifiable Random Function.
% If we compare with group signatures, our notion is also more general than the
% conventional one, again for the same reason as sign unforgeability (i.e., \Open
% can return any value, not just the signer's identity). Thus, the need to extract
% the signer's data in order to detect if a framing has taken place.

@@

\begin{description}
\item[$\NIZKRel_{\Issue}$:] Set by issuers, governs via \fissue the rules for
  issuing new credentials. It is defined as $\NIZKRel_{\Issue} = \lbrace
  (\usk,\scred,\attrs_{\scred},r), (\Ccom,\attrs,\sipk_{\scred}): \Ccom =
  \CCommit(usk;r) \land \fissue(\usk,\scred,\attrs) = 1 \land \forall \cred \in
  \scred, \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1 \rbrace$,
  where for readability we write $\attrs_{\scred}$ as abbreviation for $\lbrace
  \attrs_{\cred} \rbrace_{\cred \in \scred}$, and similarly for $\sipk_{\scred}$.
  Basically, this relation requires that, in order to issue a credential with
  attribtes \attr, and bound to \usk, the requester has to commit to \usk and
  prove knowledge of it, as well as prove that all additional credentials needed
  for the issuing to be granted, meet some defined policy \fissue.
\item[$\NIZKRel_{\Sign}$:] Can be set by anyone but, for simplicity, assume
  verifiers define them. Governs via \feval and \finsp what utility
  information is directly revealed by signatures, or extracted by openers.
  It is defined as $\NIZKRel_{\Sign} = \lbrace (\usk,\scred,
  \attrs_{\scred},\yeval^1,\yinsp,r,r'),(\msg,\feval,\yeval^0,\ceval,\cinsp,
  \sipk_{\scred},\Eek,\widetilde{\Eek}): \ceval = \EEnc(\widetilde{\Eek},\yeval^1;r)
  \land \cinsp= \EEnc (\Eek,\yinsp;r') \land (\yeval^0,\yeval^1) = \feval(\usk,
  \scred,\msg) \land \yinsp = \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \land
  \forall \cred \in \scred, \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred})
  = 1) \rbrace$, with $\attrs_{\scred}$ and $\sipk_{\scred}$ as in
  $\NIZKRel_{\Issue}$. In a
  nutshell, this relation ensures that signatures will produce the correct
  signature evaluation and opening values, and that any credential used to
  create the signature is bound to the same \usk key.
\item[$\NIZKRel_{\Open}$:] Ensures that the utility information extracted by
  the \Open algorithm is correct. It is defined as $\NIZKRel_{\Open} =
  \lbrace (\osk),(\Ec,\yinsp): \yinsp = \EDec(\osk,\Ec) \rbrace$.
\end{description}

\paragraph{$\parm \gets \Setup(\secpar,\AttrSpace)$.} %
The setup process essentially consists on generating the public parameters
for all the building blocks. In detail, it parses \secpar as $(\Csecpar,
\NIZKsecpar,\SBCMsecpar,\Esecpar)$. Then, run $\Cparm \gets
\CSetup(\Csecpar)$, $\SBCMparm \gets  \SBCMSetup(\SBCMsecpar)$, $\Sparm \gets
\SSetup(\Ssecpar)$, $\Eparm \gets \ESetup(\Esecpar)$, $\NIZKcrs_{\Issue} \gets
\NIZKSetup^{\NIZKRel_{\Issue}}(\NIZKsecpar)$, $\NIZKcrs_{\Sign} \gets
\NIZKSetup^{\NIZKRel_{\Sign}}(\NIZKsecpar)$, and $\NIZKcrs_{\Open} \gets
\NIZKSetup^{\NIZKRel_{\Open}}(\NIZKsecpar)$. Return $(\Cparm,\SBCMparm,
\Sparm,\Eparm,\NIZKcrs_{\Issue},\NIZKcrs_{\Sign},\NIZKcrs_{\Open},
\AttrSpace)$. Note that many of these parameter setup algorithms can
actually be run by separate entities (respecting some commonalities like,
e.g., same pairing-friendly curves). For instance, each opener could
run its own \ESetup algorithm, or each verifier its
$\NIZKSetup^{\NIZKRel_{\Sign}}$, to advertise the signing evaluation functions
it accepts. For simplicity of exposition, we bundle them together here.

\paragraph{$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.} %
To generate its key pair, each issuer first parses \parm as $(\cdot,\SBCMparm,
\Sparm,\cdot,\cdot,\cdot,\cdot,\cdot)$. Then, runs $(\Svk,\Ssk) \gets
\SKeyGen(\Sparm)$, $(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$,
$\sig_{\fissue} \gets \SSign(\Ssk,\fissue)$, $\ipk \gets (\Svk,\fissue,
\sig_{\fissue})$, $\isk \gets \Ssk$ and return $(\ipk,\isk)$.

>>>>

The main contribution of this section is giving a simple syntax and model that
still allow spanning a wide variety of related schemes. We combine aspects of GS
and AC schemes, generalizing whenever possible. Like in ACs, there are multiple
issuers, and each user can get one or more credentials from any of them; and,
also, use more than one credential simultaneously to produce a signature. We
incorporate openers, as in GSs, but there is no tight relationship between
issuer and opener. As a consequence, signers (potentially along with verifiers)
may choose, on a per-signature basis, the policies governing the utility
information extractable from a signature. Finally, we incorporate functions that
allow tweaking the conditions checked at credential issuance and signature
generation times, including the information that an opener will be able to
extract from a signature. This flexibilizes the scheme even beyond the loose
relationship between issuer and opener.

@@

\begin{definition}{(\CUASGen restrictions)}
  \label{def:uas-restrictions}
  Let \CUASGen be a generic construction of an \UAS scheme, secure according to
  the model defined in \secref{ssec:model-uas}, and three functions $\fissue^a$,
  $\feval^b$, $\finsp^c$ compatible with the previous definitions. We say that
  \CUASGen, instantiated with $\fissue^a$, $\feval^b$, and $\finsp^c$, is a
  $(\fissue^a,\feval^b,\finsp^c)$-restriction of \CUASGen.
\end{definition}

@@

\paragraph{Anonymity.} %
Users may see their privacy compromised through their interactions with issuers
to request a credential, or via the signatures they produce. Thus, we define two
games to define the privacy expected in those situations.

The issuance anonymity game captures that, given polymomially many
credential issuance interactions, the adversary gains no information about the
user(s) behind them. For this, we allow the adversary to control targetted
issuers and openers (although it may also add honest ones), and add honest and
corrupt users. The adversary can also obtain credentials, produce signatures,
and open them. We need to make some limitations to prevent trivial wins: first,
when querying the oracle for obtaining a challenge credential out of two
possible user-credential set pairs, the issuance protocol must either succeed or
fail for both; also, the adversary can open signatures produced with credential
sets containing challenge credentials $\cred_b$, only if the output of \Open is
the same as with the complementary $\cred_{1-b}$ 
\todo{this is not done in the oracles. Fix.} (note that any other signature
can be open).
Intuitively, if the adversary cannot distinguish arbitrary runs with all oracles
(provided the previous constraint) when he gets challenge credentials $\cred_b$
from runs with credentials $\cred_{1-b}$, then the issuance protocol is
privacy-preserving.

The signature anonymity game is similar to the traditional one in GS schemes.
It captures that the signatures produced by system users do not leak information
about their identity beyond what is already revealed via $\yeval^0$ and what
may be revealed via \yinsp. Concretely, the adversary can interact with oracles
as in the issuance anonymity game, except that instead of obtaining challenge
credentials, it obtains challenge signatures. These signatures must have been
produced via the \CHALb oracle, which ensures that the $\yeval^0$ value is the
same for both input sets -- otherwise, rejects creating the signature. We also
allow opening signatures; even challenge $\cSig_b$ signatures, as long as the
\yinsp value of the counterpart $\cSig_{1-b}$ is the same. Note that this is
stronger than the traditional CCA-like security of group signatures, where no
challenge signature can be open.

@@

\begin{figure*}[htp!]
  \centering
  \scalebox{0.9}{
    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\ExpIssAnonb(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        b^* \gets \adv^{\OIssAnon} (\parm) \\
        \pcreturn b^*
      }
    \end{minipage}

    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\ExpSigAnonb(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        b^* \gets \adv^{\OSigAnon} (\parm) \\
        \pcreturn b^*
      }
    \end{minipage}
  }
  \caption{Issuance and signature anonymity experiments for \UAS schemes.}
  \label{fig:exp-uas-anonb}
\end{figure*}

@@

\paragraph{On the generality of anonymity in \UAS schemes.} %
From the point of view of the achieved privacy, depending on how one defines
\fissue, \feval and \finsp, it is easy to see that the resulting scheme would
have different privacy level. For instance, a scheme that has very granular
\feval outputs barely provides privacy. Or a scheme for which most signatures
include the same \finsp value has less accountability, but higher privacy.
%
This is a natural consequence of the fact that, with different choices of those
functions, one can mimic the behaviour of (more restricted) schemes. For
instance, by setting \finsp to output the signer's public key, and \feval to
output nothing, one gets the same anonymity as in vanilla group signatures
(concretely, no challenge signature can be opened). Or, if \feval outputs any
arbitrary subset of the attributes in the used credential(s), and \finsp outputs
any constant value, then we get the same anonymity as in conventional selective
disclosure anonymous credential schemes, where any pair of users with different
subset of revealed attributes are clearly distinguishable. The impact of \fissue
is somehow orthogonal to the previous, but can be seen as a kind of equivalent
to \feval, at issuance time.
%
Importantly, note that the model is agnostic to the concrete instantiation of
these functions, and just cares about whether their outputs are equal or not,
in order to avoid trivial wins by the adversary.

\paragraph{Unforgeability.} \UAS inherits from AC and GS schemes two different
notions of unforgeability: from AC schemes, the notion that no adversary can
prove claims unless it owns credentials with the proper attributes; from GS
schemes, that only credential owners can produce valid signatures. \UAS also
has verifiable openings as some group signature schemes, which sits somewhere
in between, and we must ensure that the values output by \Open are correct and
trace back to a user with consistent credentials. All the previous is captured
by a signature unforgeability property. We define this by allowing the adversary
to call any oracle, except the one for corrupting issuers. The adversary wins if
it produces a valid signature over some message that: (1), opens to a wrong
value, or to a value that cannot be processed by \Judge; (2), is not consistent
with the expected \Yeval value; or (3), cannot be associated to known
credentials owned by a known user.

Again, since \UAS schemes (may) require proving claims at issuance time, we
need to ensure that those claims cannot be forged by an adversary without the
proper attributes. In this case, since we (need to) assume trusted issuers, we
can condition on having the $\langle \Obtain,\Issue \rangle$ transcripts
available for analysis. Thus, the adversary -- with access to the same oracles
as above -- is challenged to output a credential identifier for a credential
that exists in \CRED and (1), the conditions required by \fissue were not
satisfied, or some of the credentials used to support the request does not
belong to the requesting user; or (2) all credentials used to support the
request are bound to the same secret key, but that secret key does not belong
to any known user. The issuance unforgeability notion formalizes this.

For both \ExpForgeIssue (in \figref{fig:exp-uas-unfor-issue}) and \ExpForgeSign
(in \figref{fig:exp-uas-unfor-sign}), the adversary is given access to the
oracle set $\Oforgeissue = \Oforgesign \gets \lbrace\HU,\CU\rbrace\GEN,\IGEN,
\OGEN,\OCORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN$.

@@

\paragraph{On the generality of unforgeability in \UAS schemes.} %
Regarding the information revealed at signature time ($\yeval^0$), \UAS's
unforgeability notion is equivalent to that of known AC schemes. It is the
generalization of the information output at opening time ($\yinsp$), only
present up to know in MPS \needcite what makes the notion of unforgeability more
subtle. The fact that multiple users may produce signatures opening to the same
value necessarily forces to generalize what is a forgery -- and, certainly,
resorting to extraction-based techniques seems unavoidable.

As for anonymity, note that by tweaking the \fissue, \feval and \finsp
functions, one can easily mimic behaviour of more restricted schemes. For
instance, \feval, along with the $\yeval^0$ output, allows revealing
authenticated attribute-related information alongside the signatures, as in AC
schemes. Or, with \fissue, rules for delegation can be easily encoded, leading
to delegatable schemes.

\paragraph{Non-frameability.} %
The notion of non-frameability in \UAS schemes is unavoidably more subtle than
in group signatures. To see this, we note that, by allowing arbitrary
evaluation and open functions to be used, it can be perfectly valid to
have a signature produced by a corrupted user output the same \yeval or \yinsp
values than the ones output when evaluating or opening a signature by an honest
user.
%
More generally, since the issuer is dishonest in non-frameability properties
and, in \UAS, the value produced by \Open may depend on the attributes
included in user credentials, the adversary may even be able to just produce
``legitimate'' openings that output any desired value. Note that this is a
relevant property, as it tells us the minimal unforgeability expectations we
can have, even against malicious issuers and openers.

In the non-frameability definition for \UAS, given in experiment \ExpNonframe in
\figref{fig:exp-uas-frame}, the adversary is challenged to produce a signature
and opening proof that is accepted by \Verify and \Judge, respectively. From
the signature, we then extract the secret data used to generate it. The
adversary wins if the signature and opening proof are accepted, but the \yeval
or \yinsp values do not match what they should be based on the extracted data;
or if the signature can be associated to the secret key of an honest user who
did not produce it (i.e., no matching call to \SIGN exists). In the game, the
adversary has access to the oracles in $\Oframe \gets
\lbrace\HU,\CU\rbrace\GEN, \lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,
\WREG,\OBTAIN,\SIGN$.

@@

\paragraph{On the generality of non-frameability in \UAS schemes.} %
The notion captured in \UAS is a sort of extension of the non-frameability
notion in group signatures, in two aspects. First, by defining a very granular
\finsp function (one that outputs the signers public key, or equivalent),
we get a scheme in which it is not possible to frame a user at all. Yet, by
defining a coarser \finsp function (e.g., one that outputs the nationality of
the signer), while framing a single user is still not possible (the checks in
lines 9 an 10 avoid it), in practice, there will be a set of ``potential
candidates to frame'' (e.g., all users of the given nationality). This can be
seen as a useful feature in many use cases, though.
%
The second aspect follows a similar reasoning, but through \feval. However, this
type of functionality revealing information at signing time is not available in
group signatures. Also, even though it is available in anonymous credentials, no
equivalent property has been considered, to the best of our knowledge. Thus,
through \UAS schemes, we extend the unforgeability expectations against corrupt
issuers, to the AC domain.

% Anonymous credentials do not have non-frameability property and, thus, it is
% hard to make a comparison. However, we can draw some connections with AC schemes
% that support revocation, as revocation is somehow equivalent to linking, which
% is a type of inspection available in group signatures. In this sense, note that
% basic revocation (without straight deanonymization) can be trivially achieved
% through our generic \Open function. For instance, one could set \finsp to
% be a pseudorandom number seeded with the user's public key (or credential). In
% this sense, \Open could be essentially seen as a Verifiable Random Function.
% If we compare with group signatures, our notion is also more general than the
% conventional one, again for the same reason as sign unforgeability (i.e., \Open
% can return any value, not just the signer's identity). Thus, the need to extract
% the signer's data in order to detect if a framing has taken place.

@@

\begin{description}
\item[$\NIZKRel_{\Issue}$:] Set by issuers, governs the rules for issuing new
  credentials. It is defined as $\NIZKRel_{\Issue} = \lbrace
  (\usk,\scred,\attrs_{\scred},r), (\Ccom,\attrs,\sipk_{\scred}): \Ccom =
  \CCommit(usk;r) \land \forall \cred \in \scred,\SBCMVerify(\ipk_{\cred},\cred,
  \usk,\attrs_{\cred}) = 1 \land \fissue(\usk,\scred,\attrs) = 1 \rbrace$,
  where for readability we write $\attrs_{\scred}$ as abbreviation for $\lbrace
  \attrs_{\cred} \rbrace_{\cred \in \scred}$, and similarly for $\sipk_{\scred}$.
  The relation requires that the owner commits to, and proves knowledge of,
  \usk. It also requires that any additional credential supporting the request
  be a valid credential (signed by some other issuer) and bound to \usk.
  Finally, the policy defined by \fissue needs to be satisfied.
\item[$\NIZKRel_{\Sign}$:] Can be set by anyone but, for simplicity, assume
  verifiers define them. Governs via \feval and \finsp what utility
  information is directly revealed by signatures, or extractable by openers.
  It is defined as $\NIZKRel_{\Sign} = \lbrace (\usk,\scred,
  \attrs_{\scred},\yeval^1,\yinsp,r,r'),(\msg,\feval,\yeval^0,\ceval,\cinsp,
  \sipk_{\scred},\Eek,\widetilde{\Eek}): \ceval = \EEnc(\widetilde{\Eek},\yeval^1;r)
  \land \cinsp= \EEnc (\Eek,\yinsp;r') \land (\yeval^0,\yeval^1) = \feval(\usk,
  \scred,\msg) \land \yinsp = \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \land
  \forall \cred \in \scred, \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred})
  = 1) \rbrace$, with $\attrs_{\scred}$ and $\sipk_{\scred}$ as in
  $\NIZKRel_{\Issue}$. In a
  nutshell, this relation ensures that signatures will produce the correct
  signature evaluation and opening values, and that any credential used to
  create the signature is bound to the same \usk key.
\item[$\NIZKRel_{\Open}$:] Ensures that the utility information extracted by
  the \Open algorithm is correct. It is defined as $\NIZKRel_{\Open} =
  \lbrace (\osk),(\Ec,\yinsp): \yinsp = \EDec(\osk,\Ec) \rbrace$.
\end{description}

Note that, besides the extensibility introduced via \fissue, \feval and
\finsp, some aspects of the previous functions could be modified (e.g., one
could require issuer public keys to be kept private). However, the previous
relations seem generic enough for a wide variety of applications.
%
From the previous relations, we define the functionality as follows:

\paragraph{$\parm \gets \Setup(\secpar,\AttrSpace)$.} %
The setup process essentially generates the public parameters for all the
building blocks. It parses \secpar as $(\Csecpar,\NIZKsecpar,\SBCMsecpar,
\Esecpar)$. Then, run $\Cparm \gets
\CSetup(\Csecpar)$, $\SBCMparm \gets  \SBCMSetup(\SBCMsecpar)$, $\Sparm \gets
\SSetup(\Ssecpar)$, $\Eparm \gets \ESetup(\Esecpar)$, $\NIZKcrs_{\Issue} \gets
\NIZKSetup^{\NIZKRel_{\Issue}}(\NIZKsecpar)$, $\NIZKcrs_{\Sign} \gets
\NIZKSetup^{\NIZKRel_{\Sign}}(\NIZKsecpar)$, and $\NIZKcrs_{\Open} \gets
\NIZKSetup^{\NIZKRel_{\Open}}(\NIZKsecpar)$. Return $(\Cparm,\SBCMparm,
\Sparm,\Eparm,\NIZKcrs_{\Issue},\NIZKcrs_{\Sign},\NIZKcrs_{\Open},
\AttrSpace)$. Many of these parameter setup algorithms can
actually be run by separate entities. For simplicity of exposition, we bundle
them together here.

\paragraph{$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.} %
Each issuer first parses \parm as $(\cdot,\SBCMparm,
\Sparm,\cdot,\cdot,\cdot,\cdot,\cdot)$. Then, runs $(\Svk,\Ssk) \gets
\SKeyGen(\Sparm)$, $(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$,
$\sig_{\fissue} \gets \SSign(\Ssk,\fissue)$, $\ipk \gets (\Svk,\fissue,
\sig_{\fissue})$, $\isk \gets \Ssk$ and return $(\ipk,\isk)$.
